### 2019-01-05 fe_px_paper/fe_body_text.tex
Added all data tables to results

% A set of measured cross sections for the various natFe(p,x), natTi(p,x), and natCu(p,x) reactions between 5–55 MeV, as well as independent measurements of isomer branching ratios, are reported.
% Figure 3 shows the 52mMn(2+)/52gMn(6+) isomer-to-ground state branching ratio for the naFe(p,αn) reaction, calculated using TALYS-v1.8 over the 20 - 55 MeV range spanned by the foil stack. It is possible to use this measurement to infer the spin cut-off σ2, the width of the angular momentum distribution of the level density [6], [7]. The isomer-to-ground state ratio lends insight into equilibrium / pre-equilibrium nature of reactions in this energy region, useful when attempting to minimize dose from an unwanted isomer/ground state of a medical radionuclide.

@@

% \caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
% \label{tab:cufe_rp_table}
% % \resizebox{\textwidth}{!}{%
% \begin{tabular}{@{}lllllll@{}}
%                             & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
% % \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
% % \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
% % \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
% % \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
% % \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
% % \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
% % \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
% % \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
% % \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
% % \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
% \ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
% % }
% \caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
% \label{tab:ti_rp_table}
% % Disable next line for journal submission
% % \resizebox{\textwidth}{!}{%
% \begin{tabular}{@{}lllllll@{}}
%                             & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
% E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
% % \ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
% % \ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
% % \ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
% % \ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
% % \ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
% % \ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
% % \ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% % \ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
% % \ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
% % \ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
% % \ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
% % \ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
% \ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
% % }
% \caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
% \label{tab:fe_ibr_table}
% \begin{tabular}{@{}lllllll@{}}
%                                & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7} 
% \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\ 
% E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
% \ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
% \ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule

>>>>

% A set of measured cross sections for the various natFe(p,x), natTi(p,x), and natCu(p,x) reactions between 5–55 MeV, as well as independent measurements of isomer branching ratios, are reported.
% Figure 3 shows the 52mMn(2+)/52gMn(6+) isomer-to-ground state branching ratio for the naFe(p,αn) reaction, calculated using TALYS-v1.8 over the 20 - 55 MeV range spanned by the foil stack. It is possible to use this measurement to infer the spin cut-off σ2, the width of the angular momentum distribution of the level density [6], [7]. The isomer-to-ground state ratio lends insight into equilibrium / pre-equilibrium nature of reactions in this energy region, useful when attempting to minimize dose from an unwanted isomer/ground state of a medical radionuclide.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:cufe_rp_table}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllllllllllll@{}}
\toprule
                            & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15} 
E$_\text{p}$ (MeV)&	\makecell{53.04\\$\pm$0.61} &	\makecell{46.18\\$\pm$0.68} &	\makecell{38.42\\$\pm$0.79} &	\makecell{34.06\\$\pm$0.86} &	\makecell{29.21\\$\pm$0.97} &	\makecell{23.6\\$\pm$1.2} &	\makecell{21.70\\$\pm$0.33} &	\makecell{18.30\\$\pm$0.38} &	\makecell{16.6\\$\pm$1.5} &	\makecell{15.38\\$\pm$0.44} &	\makecell{13.11\\$\pm$0.49} &	\makecell{10.57\\$\pm$0.57} &	\makecell{6.90\\$\pm$0.82} &	\makecell{1.4\\$\pm$1.0}\\ \midrule
\ce{^{54}Mn}\,($\sigma_i$)&	\makecell{2.048\\$\pm$0.072} &	\makecell{0.408\\$\pm$0.012} &	\makecell{0.0931\\$\pm$0.0034} &	\makecell{0.0517\\$\pm$0.0017} &	\makecell{0.02233\\$\pm$0.00075} &	\makecell{0.01848\\$\pm$0.00065} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{57}Ni}\,($\sigma_c$)&	\makecell{2.107\\$\pm$0.094} &	\makecell{0.738\\$\pm$0.024} &	\makecell{0.0530\\$\pm$0.0033} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{57}Co}\,($\sigma_i$)&	\makecell{48.8\\$\pm$2.2} &	\makecell{32.2\\$\pm$1.5} &	\makecell{3.79\\$\pm$0.37} &	\makecell{1.206\\$\pm$0.046} &	\makecell{1.673\\$\pm$0.063} &	\makecell{1.053\\$\pm$0.046} &	\makecell{0.707\\$\pm$0.033} &	\makecell{0.264\\$\pm$0.025} &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{57}Co}\,($\sigma_c$)&	\makecell{50.9\\$\pm$2.2} &	\makecell{33.0\\$\pm$1.5} &	\makecell{3.84\\$\pm$0.37} &	\makecell{1.206\\$\pm$0.046} &	\makecell{1.673\\$\pm$0.063} &	\makecell{1.053\\$\pm$0.046} &	\makecell{0.707\\$\pm$0.033} &	\makecell{0.264\\$\pm$0.025} &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{60}Co}\,($\sigma_c$)&	\makecell{9.22\\$\pm$0.33} &	\makecell{7.70\\$\pm$0.25} &	\makecell{6.14\\$\pm$0.23} &	\makecell{3.12\\$\pm$0.13} &	\makecell{0.794\\$\pm$0.043} &	\makecell{0.201\\$\pm$0.014} &	\makecell{0.1252\\$\pm$0.0086} &	\makecell{0.0199\\$\pm$0.0020} &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{60}Cu}\,($\sigma_c$)&	\makecell{24.84\\$\pm$0.89} &	\makecell{16.06\\$\pm$0.52} &	\makecell{1.461\\$\pm$0.095} &	\makecell{0.578\\$\pm$0.021} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{61}Co}\,($\sigma_c$)&	\makecell{4.18\\$\pm$0.49} &	\makecell{5.69\\$\pm$0.57} &	\makecell{6.94\\$\pm$0.49} &	\makecell{6.61\\$\pm$0.60} &	\makecell{5.94\\$\pm$0.76} &	\makecell{0.872\\$\pm$0.067} &	\makecell{0.2531\\$\pm$0.0085} &	\makecell{0.1178\\$\pm$0.0043} &	\makecell{0.0411\\$\pm$0.0024} &	-- &	-- &	-- &	-- &	--\\
\ce{^{61}Cu}\,($\sigma_c$)&	\makecell{78\\$\pm$78} &	\makecell{101\\$\pm$101} &	\makecell{161\\$\pm$161} &	\makecell{155\\$\pm$155} &	\makecell{104\\$\pm$104} &	\makecell{7.0\\$\pm$7.0} &	\makecell{1.8\\$\pm$1.8} &	\makecell{1.2\\$\pm$1.2} &	\makecell{0.80\\$\pm$0.80} &	-- &	-- &	-- &	-- &	--\\
\ce{^{64}Cu}\,($\sigma_i$)&	\makecell{49.9\\$\pm$1.8} &	\makecell{52.7\\$\pm$1.8} &	\makecell{58.4\\$\pm$2.1} &	\makecell{62.4\\$\pm$2.2} &	\makecell{101.8\\$\pm$3.7} &	\makecell{145\\$\pm$11} &	\makecell{83.1\\$\pm$2.8} &	\makecell{57.0\\$\pm$1.9} &	\makecell{45.9\\$\pm$2.0} &	\makecell{22.15\\$\pm$0.92} &	-- &	-- &	-- &	--\\ \bottomrule
\end{tabular}
}
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:ti_rp_table}
\small
% Disable next line for journal submission
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllllllllllll@{}}
\toprule
                            & \multicolumn{14}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-15} 
E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\  \midrule
\ce{^{43}K}\,($\sigma_c$)&	\makecell{1.549\\$\pm$0.080} &	\makecell{0.889\\$\pm$0.056} &	\makecell{0.189\\$\pm$0.014} &	\makecell{0.0462\\$\pm$0.0035} &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	-- &	--\\
\ce{^{44g}Sc}\,($\sigma_i$)&	\makecell{25.0\\$\pm$2.0} &	\makecell{27.0\\$\pm$1.9} &	\makecell{37.0\\$\pm$2.3} &	\makecell{52.6\\$\pm$3.9} &	\makecell{47.8\\$\pm$2.9} &	\makecell{29.9\\$\pm$2.6} &	\makecell{8.09\\$\pm$0.27} &	\makecell{3.49\\$\pm$0.13} &	\makecell{2.70\\$\pm$0.27} &	\makecell{3.02\\$\pm$0.12} &	\makecell{2.49\\$\pm$0.11} &	-- &	-- &	--\\
\ce{^{44m}Sc}\,($\sigma_i$)&	\makecell{12.60\\$\pm$0.41} &	\makecell{12.37\\$\pm$0.36} &	\makecell{15.20\\$\pm$0.52} &	\makecell{17.78\\$\pm$0.57} &	\makecell{16.85\\$\pm$0.55} &	\makecell{8.63\\$\pm$0.30} &	\makecell{4.26\\$\pm$0.15} &	\makecell{1.451\\$\pm$0.051} &	\makecell{1.317\\$\pm$0.052} &	\makecell{1.269\\$\pm$0.049} &	\makecell{0.839\\$\pm$0.036} &	-- &	-- &	--\\
\ce{^{44}Sc}\,($\sigma_c$)&	\makecell{37.6\\$\pm$2.1} &	\makecell{39.4\\$\pm$1.9} &	\makecell{52.2\\$\pm$2.3} &	\makecell{70.4\\$\pm$3.9} &	\makecell{64.7\\$\pm$3.0} &	\makecell{38.6\\$\pm$2.7} &	\makecell{12.35\\$\pm$0.31} &	\makecell{4.94\\$\pm$0.14} &	\makecell{4.02\\$\pm$0.27} &	\makecell{4.29\\$\pm$0.13} &	\makecell{3.33\\$\pm$0.11} &	-- &	-- &	--\\
\ce{^{47}Sc}\,($\sigma_c$)&	\makecell{21.20\\$\pm$0.68} &	\makecell{20.45\\$\pm$0.57} &	\makecell{21.66\\$\pm$0.76} &	\makecell{23.55\\$\pm$0.75} &	\makecell{25.12\\$\pm$0.84} &	\makecell{15.63\\$\pm$0.55} &	\makecell{11.53\\$\pm$0.48} &	\makecell{5.50\\$\pm$0.20} &	\makecell{2.75\\$\pm$0.11} &	\makecell{1.569\\$\pm$0.058} &	\makecell{0.810\\$\pm$0.034} &	\makecell{0.361\\$\pm$0.012} &	\makecell{0.218\\$\pm$0.015} &	--\\
\ce{^{48}Sc}\,($\sigma_i$)&	\makecell{1.66\\$\pm$0.10} &	\makecell{1.68\\$\pm$0.17} &	\makecell{1.29\\$\pm$0.14} &	\makecell{0.772\\$\pm$0.051} &	\makecell{0.700\\$\pm$0.052} &	\makecell{0.339\\$\pm$0.020} &	\makecell{0.318\\$\pm$0.011} &	\makecell{0.1852\\$\pm$0.0095} &	\makecell{0.135\\$\pm$0.012} &	\makecell{0.0625\\$\pm$0.0037} &	-- &	-- &	-- &	--\\ \bottomrule
\end{tabular}
}
\end{table}

% \ce{^{nat}Cu}(p,x)\ce{^{52}Mn}
\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x) and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
\label{tab:fe_ibr_table}
                               & \multicolumn{14}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-15} 
\ce{^{nat}Fe}(p,x)\ce{^{52}Mn} &	\makecell{0.417\\$\pm$0.022} &	\makecell{0.414\\$\pm$0.024} &	\makecell{0.396\\$\pm$0.026} &	\makecell{0.388\\$\pm$0.021} &	\makecell{0.517\\$\pm$0.026} &	\makecell{0.420\\$\pm$0.025} &	\makecell{0.358\\$\pm$0.018} &	\makecell{0.202\\$\pm$0.010} &	\makecell{0.404\\$\pm$0.043} &	\makecell{0.638\\$\pm$0.043} &	\makecell{0.915\\$\pm$0.073} &	-- &	-- &	--\\
\ce{^{nat}Fe}(p,x)\ce{^{58}Co} &	-- &	-- &	-- &	\makecell{0.326\\$\pm$0.017} &	\makecell{0.387\\$\pm$0.020} &	\makecell{0.485\\$\pm$0.025} &	\makecell{0.583\\$\pm$0.033} &	\makecell{0.614\\$\pm$0.034} &	\makecell{0.420\\$\pm$0.026} &	\makecell{0.486\\$\pm$0.036} &	\makecell{0.341\\$\pm$0.024} &	\makecell{0.299\\$\pm$0.016} &	\makecell{0.234\\$\pm$0.015} &	\makecell{0.214\\$\pm$0.029}         \vspace{1em}     \\ 
E$_\text{p}$ (MeV)&	\makecell{53.31\\$\pm$0.61} &	\makecell{46.48\\$\pm$0.68} &	\makecell{38.76\\$\pm$0.78} &	\makecell{34.44\\$\pm$0.86} &	\makecell{29.63\\$\pm$0.96} &	\makecell{24.1\\$\pm$1.1} &	\makecell{22.29\\$\pm$0.32} &	\makecell{18.98\\$\pm$0.37} &	\makecell{17.3\\$\pm$1.5} &	\makecell{16.14\\$\pm$0.42} &	\makecell{14.03\\$\pm$0.47} &	\makecell{11.49\\$\pm$0.55} &	\makecell{8.38\\$\pm$0.70} &	\makecell{2.88\\$\pm$0.88}\\ \midrule
\ce{^{nat}Ti}(p,x)\ce{^{44}Sc} &	\makecell{0.335\\$\pm$0.022} &	\makecell{0.314\\$\pm$0.018} &	\makecell{0.291\\$\pm$0.016} &	\makecell{0.253\\$\pm$0.016} &	\makecell{0.260\\$\pm$0.015} &	\makecell{0.224\\$\pm$0.017} &	\makecell{0.345\\$\pm$0.015} &	\makecell{0.294\\$\pm$0.013} &	\makecell{0.328\\$\pm$0.026} &	\makecell{0.296\\$\pm$0.015} &	\makecell{0.252\\$\pm$0.014} &	-- &	-- &	--\\\bottomrule
